pema application

### 2022-12-05 paper/manuscript.Rmd
fixed typos

<span id = "rsquared">Our primary performance indicator was predictive performance,
a measure of model generalizability.
To compute it, for each iteration of the simulation,
both a training data set and a testing data set are generated from the same known population model.
The number of cases in the training data vary according to the design factors of the simulation study.
The number of cases in the testing data set was always 100.
The models under evaluation (BRMA, RMA) were estimated on the training data,
and used to predict cases in the testing data.
Predictive performance was operationalized as the model's explained variance in the testing data, $R^2_{test}$, calculated as follows:
$$
R_{test}^{2} = 1- \frac{\sum_{i=1}^{k}(y_{i,test}-\hat{y}_{i,test})^{2}}{\sum_{i=1}^{k}(y_{i,test}-\bar{y}_{train})^{2}}
$$
Where $k$ is the number of studies in the testing data set, $\hat{y}_{i-test}$ is the predicted effect size for study $i$, and $\bar{y}_{train}$ is the mean of the training data.
The $R^2_{test}$ differs from the familiar $R^2$ metric:
$R^2$ describes the proportion of variance a model explains in the training data, and it always increases as the model becomes more complex.
By contrast, $R^2_{test}$ reflects the explained variance in the testing data.
Remember that BRMA was developed to reduce the risk of overfitting meta-regression models.
The $R^2_{test}$ is a useful metric to detect overfitting,
which causes it to decrease, or even become negative.
</span>

@@

<span id = "sensitivityanalysis">All simulations were conducted with default settings for the model's prior distributions, based on prior research [@vanErpOberskiMulder2019; @PiironenVehtari2017b].
Our results suggest that these defaults are suitable for a wide range of situations, including when model assumptions are violated.
However, bear in mind that model parameters are influenced by the prior distribution.
It is good practice to perform sensitivity analysis to determine how sensitive the model results and inferences are to different prior specifications. 
Performing sensitivity analyses is particularly important when the sample is small,
as in this case, the prior is more influential.</span>

>>>>

<span id = "rsquared">Our primary performance indicator was predictive performance,
a measure of model generalizability.
To compute it, for each iteration of the simulation,
both a training data set and a testing data set are generated from the same known population model.
The number of cases in the training data vary according to the design factors of the simulation study.
The number of cases in the testing data set was always 100.
The models under evaluation (BRMA, RMA) were estimated on the training data,
and used to predict cases in the testing data.
Predictive performance was operationalized as the model's explained variance in the testing data, $R^2_{test}$, calculated as follows:
$$
R_{test}^{2} = 1- \frac{\sum_{i=1}^{k}(y_{i,test}-\hat{y}_{i,test})^{2}}{\sum_{i=1}^{k}(y_{i,test}-\bar{y}_{train})^{2}}
$$
Where $k$ is the number of studies in the testing data set, $\hat{y}_{i-test}$ is the predicted effect size for study $i$, and $\bar{y}_{train}$ is the mean of the training data.
The $R^2_{test}$ differs from the familiar $R^2$ metric:
$R^2$ describes the proportion of variance a model explains in the training data, and it always increases as the model becomes more complex.
By contrast, $R^2_{test}$ reflects the explained variance in the testing data.
Recall that BRMA was developed to reduce the risk of overfitting meta-regression models.
The $R^2_{test}$ is a useful metric to detect overfitting,
which causes it to decrease, or even become negative.
</span>

@@

<span id = "sensitivityanalysis">All simulations were conducted with default settings for the model's prior distributions, based on prior research [@vanErpOberskiMulder2019; @PiironenVehtari2017b].
Our results suggest that these defaults are suitable for a wide range of situations, including when model assumptions are violated.
However, bear in mind that model parameters are influenced by the prior distribution.
It is good practice to perform a sensitivity analysis to determine how sensitive the model results and inferences are to different prior specifications. 
Performing sensitivity analyses is particularly important when the sample is small,
as in this case, the prior is more influential.</span>
